---
title: Presentations with Xaringan
author: Peter Baumgartner
date: '2018-07-18'
categories:
  - demo
  - slides
tags:
  - blogdown
  - hugo-academic
  - xaringan
slug: presentations-with-xaringan
authors:
  - Peter Baumgartner
draft: no
header:
  caption: ''
  image: ''
  preview: yes
summary: This files demonstrate how to present slideshows with the Xaringan package. I am following in this short post the detailed `description` by [Tim Mastny](https://timmastny.rbind.io/blog/embed-slides-knitr-blogdown/). 
---

## Demo of the Xaringan package

I am following here the blog entry by [Tim Mastny](https://timmastny.rbind.io/blog/embed-slides-knitr-blogdown/).

### Refer to an external slide show

```{r}
knitr::include_url('https://timmastny.rbind.io/slides/first_presentation', height = "505px")
```

### Refer to an internal slide show


```{r}
knitr::include_url('/slide/xaringan-demo.html', height = "505px")
```

The parameter `height = "505px"` prevents the gray frames around the slides. To tweak this I had to experiment with the best pixel value. (Maybe there is a better way to tweak this parameter with the right value, e.g. taking the value from the css.)

### Refer to the file with RMarkdown itself

![](/slide/xaringan-demo.html)

With this themes it generates a kind of a thumbnail. With other themes I have got other sizes, e.g. over the whole widht of the text column. I believe that this has to be settled in one of the css files (`layout/partials/css` or `layout/index.css`).

### Most important: A link to the full screen presenation

https://portfolio.peter-baumgartner.net/slide/xaringan-demo#1
