---
title: Presentations with Xaringan
author: Peter Baumgartner
date: '2018-07-18'
categories:
  - demo
  - slides
tags:
  - blogdown
  - hugo-academic
  - xaringan
slug: presentations-with-xaringan
authors:
  - Peter Baumgartner
draft: no
header:
  caption: ''
  image: ''
  preview: yes
summary: This short demo files demonstrate how to present slideshows with the `Xaringan` package.
---

## Demo of the Xaringan package

I am following in this short post the detailed description by [Tim Mastny](https://timmastny.rbind.io/)  in his blog entry [Embed Slides in Your Blog](https://timmastny.rbind.io/blog/embed-slides-knitr-blogdown/). Please read his article to understand the installation procedure.


### Refer to an external slide show

```{r}
knitr::include_url('https://timmastny.rbind.io/slides/first_presentation')
```

### Refer to an internal slide show


```{r}
knitr::include_url('/slide/xaringan-demo.html', height = "505px")
```

### Summary

Both example above are the same as in Tim's article. 

**Two observations:**

1. There is not need to load the Xaringan package with `library(xaringan)`. At the moment do not understand, why this is unnecessary. 
2. In the second example the gray left and right margin has disappeared. The parameter `height = "505px"` does this. To tweak this I had to experiment with the optimal pixel value. (Maybe there is a better way to tweak this parameter with the right value, e.g. taking the value from the css.) 

The height paramter solves one of the problem mentioned by Tim:

> I’m also investigating to see if I can trim the iframe so I only see the slides and not the gray bars on the side.


## Display the slides in full screen view

Here I wanted to address his second issue:

> I’d like to be able to use a relative reference to the slideshow’s HTML file in the static/ directory, but I think knitr::include_url() requires a live URL. I’ll have to do more research.

### My first try: Using the Markdown image code 

My first try was: `![](/slide/xaringan-demo.html/#5)`

![](/slide/xaringan-demo.html#5)

It generates a kind of a thumbnail. Maybe this is theme dependent. I once tried it out in another theme and got other sizes, e.g. over the whole widht of the text column. I believe that this has to be settled in one of the css files (`layout/partials/css` or `layout/index.css`). 

A kind of a thumbnail was not the result I was looing for, but it could become handy anyway. For instance as a reference in an article. With the slide number behind the URL one can reference directly every slide frame.

### My second try: Usind Markdown with an absolute link

The second try is a [link in standard markdown](https://portfolio.peter-baumgartner.net/slide/xaringan-demo#1) to the file. It opens up the full screen presentation. The code I have used was:

`The second try is a [link in standard markdown](https://portfolio.peter-baumgartner.net/slide/xaringan-demo#1) to the file.`

This is not ideal as one cannot test it locally and needs always an internet connection for the presentation.

### My third try: Using Hugo shortcode for a relative link

{{% staticref "files/Benennung-Baumgartner.pdf" "newtab" %}}Download my CV{{% /staticref %}}

The third try is a {{% staticref "files/Benennung-Baumgartner.pdf" "newtab" %}}relative link with Hugo shortcodes{{% /staticref %}} to the file. It opens up the full screen presentation in a new tab. The code I was using is:

`The third try is a {{% staticref "slide/xaringan-demo.html" "newtab" %}}relative link with Hugo shortcodes{{% /staticref %}} to the file.`

This is not the exactly the solution Tim was looking for. But it is near enough. Now one can present the slide show without an internet connection. --- I tried, but I could not manage to create with Markdwon a working relative link to the full screen presentation.

***

To inspect the the full code of this post look at [my repo at GitHub](https://github.com/petzi53/weblog-portfolio).
